Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-27 draft/ms_v5.tex
Final version; Jim-->James

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie

@@

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{2, 4},
        Jim Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{2},
        Steven Bickerton \altaffilmark{2},
        Satoshi Miyazaki \altaffilmark{6}, 
        Jean Coupon \altaffilmark{7},
        HSC Collaboration \altaffilmark{8}}
%% ------------------------------------------------------------------------------------ %%

>>>>

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie
% Version 5; Edits from Alexie; Comments by Jim

@@

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{2, 4},
        James Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{2},
        Steven Bickerton \altaffilmark{2},
        Satoshi Miyazaki \altaffilmark{6}, 
        Jean Coupon \altaffilmark{7},
        HSC Collaboration \altaffilmark{8}}
%% ------------------------------------------------------------------------------------ %%
